### 2017-03-24 errana.tex
proof finished

%!TEX root =  autocontgrlp.tex
\section{Proof of \cref{cmt2}}\label{sec:improv}
In this section we present the proof of the main result, \cref{cmt2}. 
The proof uses contraction-arguments. 
\newcommand{\G}{\Gamma}
We will introduce two novel contraction operators, $\G,\hg: \Re^S \to \Re^S$, that capture the distortion introduced
by the extra constraint in ALP and the relaxation in LRALP, respectively. 
Then we relate the solution of LRALP to the fixed point of $\hg$.

Note that for the proof it suffices to consider the case when $\Jlro$ is finite-valued because otherwise the bound is vacuous.
Also, recall that it was assumed that $\psi$ lies in the column space of $\Phi$, while $\beta_\psi$, the $\alpha$-discounted stability of $\psi$ w.r.t. the MDP (cf. \eqref{eq:betadef}) is strictly below one. 
We also assumed that the matrix $W$ is nonnegative valued, while $c$ specifies a probability distribution over $\S$: $\sum_s c(s) = 1$ and $c\in \R_+^S$.

The operators $\G,\hg$ are defined as follows: For $J\in \Re^S$, $s\in \S$,
\begin{align*}
(\G J)(s) & = \min\{ r^\top \phi(s) \,:\, \Phi r \ge T J ,\, r\in \Re^k \}\,,\\
(\hg J)(s) & = \min\{ r^\top \phi(s) \,:\, W^\top E \Phi r \ge W^\top E H J ,\, r\in \Re^k\}\,.
\end{align*}
Note that $(\G J)(s)$ mimics the definition of ALP with $c = e_s$, except that the constraint $J = \Phi r$ is dropped.
The same holds for $\hg$ in relation to LRALP.
Letting $\F(J) = \{ \Phi r\,:\, \Phi r \ge T J, r\in \Re^k \}$ be the \emph{common} feasible set of the LP defining $(\G J)(s)$.
It follows that for any $V\in \F(J)$, $V \ge \Gamma J$. Further, $\Gamma J \ge T J$.

Let us now recall some basic results from the theory of contraction maps.
First, let us recall the definition of contractions. Let $\norm{\cdot}$ be a norm on $\Re^S$ and $\rho>0$.
We say that the map $B: \Re^S \to \Re^S$ is $(\rho,\norm{\cdot})$-Lipschitz if for any $J,J'\in \Re^S$, $\norm{ BJ - BJ' } \le \rho \norm{J-J'}$. We say that $B$ is a \emph{$\norm{\cdot}$-contraction} with factor $\rho$ 
if it is $(\rho,\norm{\cdot})$-Lipschitz and $\rho<1$. It is particularly easy to check whether a map is a contraction map with respect to a weighted maximum norm 
if it is known to be \emph{monotone}.
Here, $B$ is said to be monotone if for any $J\le J'$, $J,J'\in \R^S$, $BJ \le BJ'$ also holds, where $\le$ is the componentwise
partial order between vectors. We start with the following characterization of monotone contractions with respect to weighted maximum norms: 
\begin{lemma}
\label{lem:maxnormmn}
Let $B:\R^S \to \R^S$, $\psi: \S \to \R_{++}$, $\beta\in (0,1)$.
The following are equivalent:
\begin{enumerate}[(i)]
\item $B$ is a monotone contraction map with contraction factor $\beta$ with respect to $\norm{\cdot}_{\psi,\infty}$.
\label{lem:item:mc}
\item For any $J,J'\in \R^S$, $d\ge 0$, $J \le J' + d \psi$ implies that $BJ \le BJ' + \beta d \psi$.
\label{lem:item:iq}
\end{enumerate}
\end{lemma}
%The proof, which essentially copies Lemma 3.1 of \cite{Kall17}, is given for completeness:
\begin{proof}
The proof is  trivial modification of the proof of Lemma 3.1 of \cite{Kall17} and is thus left as an exercise.
\if0
%Note first that for any $\eps\ge 0$, $-\eps \psi \le J - J' \le \eps \psi$ implies that $\norm{J-J'}_{\mn} \le \eps$.
Introduce $\cdot$ to denote elementwise products: Thus, $(\psi \cdot J)(s) = \psi(s) J(s)$. 
We also let $\psi^{-1}(s) = 1/\psi(s)$ and we will use the shorthand $\norm{\cdot} = \norm{\cdot}_{\mn}$.

Let us first prove \eqref{lem:item:mc} $\Rightarrow $ \eqref{lem:item:iq}. 
Thus, assume that $B$ is a monotone contraction
map with factor $\beta$. Take any $J,J'$, $d>0$, $J \le J'+ d\psi$. 
We have $BJ = B(J + d \psi) - B J' + B J' \le (\psi^{-1} \cdot (B(J + d \psi) - B J' ))\cdot \psi + BJ'
\le \norm{B(J+d\psi) - BJ'} \psi + BJ' \le \beta d \norm{J-J'} \psi +  BJ'$.

For the reverse direction, note that monotinicity follows by taking $d=0$.
Now, let $\eps = \norm{J-J'}$. Then, $J \le J'+ \eps \psi$ and $J' \le J+\eps \psi$.
By monotonicity and the assumed property of $B$ (using $d=\eps\ge 0$), 
$-\beta \eps \psi \le BJ - BJ' \le \beta \eps \psi$, which implies
that $\norm{BJ - BJ'} \le \beta$.
\fi
\end{proof}
\begin{corollary}
\label{maxnormmn}
\label{cor:maxnormmn}
If $B$ is monotone and there exists some $\beta\in [0,1)$ such that for any $J\in \Re^S$ and $d>0$,
\begin{align}
\label{eq:shiftmn}
B( J + d \psi) \le B J + \beta d \psi
\end{align} 
then $B$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta$.
\end{corollary}
\begin{proof}
Let $J,J'\in \R^S$, $d\ge 0$ and assume that $J\le J' + d \psi$. By monotonicity $BJ \le B(J'+ d \psi)$, while
by~\eqref{eq:shiftmn}, $B(J'+d\psi) \le BJ' + \beta d \psi$. Hence, $BJ \le BJ' + \beta d \psi$. 
This shows that \eqref{lem:item:iq} of \cref{lem:maxnormmn} holds. Hence, by this lemma, $B$ is a contraction with factor $\beta$ with respect to $\norm{\cdot}_{\mn}$.
\end{proof}
\if0
\begin{proof}
First, we show that for any $t\ge 0$,  $J\in \Re^n$,
$B( J - t \psi) \ge B J - \beta t \psi$ also holds.
To see this define $J' = J-t\psi$. Then, $J = J'+t\psi$, hence $B J \le B J' + \beta t \psi$. Reordering this inequality gives the result.
Let $\eps = \norm{J_1 - J_2}_{\mn}$, where $J_1,J_2\in \Re^n$ are arbitrary.
Then $J_2 - \eps \psi \le J_1 \le J_2 + \eps \psi$. 
By the monotonicity of $B$,
$B(J_2 - \eps \psi) \le B J_1 \le B(J_2 + \eps \psi)$. 
Using~\eqref{eq:shiftmn}, we get 
$B J_2 - \beta \eps \psi \le B J_1 \le B J_2 + \beta \eps \psi$, i.e., $-\beta \eps \psi \le B J_1 - B J_2 \le \beta \eps \psi$, from which the result follows.
\end{proof}
\fi

@@

Let us now return to the proof of our main result. Recall that the goal is to bound 
$\norm{J^*-\Jlr}_{1,c}$ through relating this deviations from the fixed point of $\hg$, which was promised to be a contraction.
Let us thus now prove this.
%\emph{Since all $1$-norms will use the same weighting $c$, we will abbreviate $\norm{\cdot}_{1,c}$ to $\norm{\cdot}_1$. Similarly, since all maximum norms use the same weighting $\psi$, we will abbreviate $\norm{\cdot}_{\infty,\psi}$ to $\norm{\cdot}_{\infty}$.}
For this, it suffices to show that $\hg$ satisfies the conditions of \cref{cor:maxnormmn}.
In fact, we will see this holds with $\beta =\beta_\psi$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{lemma}\label{tgmonotone}\label{gshiftmn}
The operator satisfies the conditions of \cref{cor:maxnormmn} with $\beta =\beta_\psi$, and is thus a 
$\norm{\cdot}_{\mn}$-contraction with coefficient $\beta_\psi$. 
%For $J_1, J_2\in \Re^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.
\end{lemma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proof}
First, recall that $H$ is monotone (all 
the $P_a$ matrices in the definition of $H$ are nonnegative valued) 
and that it satisfies an inequality similar to \eqref{eq:shiftmn}: For any $t\ge 0$, $J\in \R^S$,
\begin{align}\label{eq:psilin}
\begin{split}
%T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi,\\
H(J+ t \psi ) \le HJ + E \beta_{\psi}\,t\,  \psi\,.
\end{split}
\end{align}

Let us now prove that $\hg$ is monotone. 
Given $J\in \Re^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N'\,\}\,$. Choose any $i\in \{1, \ldots, n\}$. Since $J_1\leq J_2$, from $W$ is nonnegative valued and $H$ is monotone, 
%\Cref{tprop}-\eqref{monotone} and \cref{grlpassmp}-\eqref{wassmp} 
it follows that $W^\top H J_1\leq W^\top H J_2$. Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\hg J_1)(i) \le (\hg J_2)(i)$.  Since $i$ was arbitrary, monotonicity of $\hg$ follows.

Let us now turn to proving that \eqref{eq:shiftmn} holds with $\beta =\beta_\psi$.
By definition, for $1\le i \le n$, $(\hg (J+t\psi) )(i) = \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top H(J+t\psi), r\in \N' \}$.
By \eqref{eq:psilin}, as $t>0$, $H(J+t\psi) \le HJ + t \beta_\psi \psi$ and hence $W^\top H(J+t\psi) \le W^\top (HJ + t \beta_\psi \psi)$. Thus,
$(\hg (J+t\psi) )(i) \le 
 \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top HJ+t\beta_\psi \psi), r\in \N' \}$.
Now, using \Cref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $d=e_i\Phi$, $b_0=t\beta_\psi \psi$
and $x_0=t \beta_\psi r_0$, the statement follows since $A x_0 = b_0$ (from \cref{grlpassmp}-\eqref{lyap}) and $\N' = \N' + \alpha t r_0$ (from \cref{grlpassmp}-\eqref{ass:n4}).
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Now, recall further that if $B:\R^S \to \R^S$ is a $(\beta,\norm{\cdot})$-contraction then it has a unique fixed point $J^*_B\in \R^S$ (i.e., $B J^*_B= J^*_B$). Further, for any $J\in \R^S$,
\begin{align}
\label{eq:csdw}
\frac{\norm{J-J^*_B}}{1-\beta} \le \norm{ BJ - J } \le (1+\beta) \norm{J-J^*_B}\,.
\end{align}
That is, $\norm{BJ-J}$ is closely tied to the distance of $J$ from $J^*_B$.%
\footnote{This is also a standard result. The upper bound can be obtained using a triangle inequality and exploiting that $J^*_B$ is a fixed point of $B$ which is a contraction. The lower bound follows by writing $J - J^*_B = (\sum_{k=0}^n B^k J - B^{k+1} J ) + B^{n+1} J - B^{n+1} J^*_B$, taking norms using the triangle inequality together with the contraction property of $B$ and finally letting $n\to \infty$.}
We will repeatedly apply this inequality.

Let $\hv$ be the fixed point $\hg$.
Then, by the triangle inequality,
\begin{align*}
\norm{J^*-\Jlr}_{1,c} \le \norm{J^*-\hv}_{1,c} +\norm{\hv-\Jlr}_{1,c}\,.
\end{align*}
Let us first bound the second term. Recall that $\Jlr = \Phi \rlr$.
We claim the following:
\begin{lemma}
aaa
\end{lemma}

\if0
We note in passing that if \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \Re^n$ and $t>0$,
\begin{align}\label{eq:psilin}
\begin{split}
T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi,\\
H(J+ t \psi ) \le HJ + E \beta_{\psi}\,t\,  \psi\,.
\end{split}
\end{align}
\fi
%\input{schematic}
The next lemma is elementary, but will prove to be useful:
\begin{lemma}\label{lpsol}
Let $A\in \Re^{u\times v}$, $b\in \Re^u,d\in \Re^v$ and $b_0=Ax_0$ for
some $x_0 \in \Re^v$, $\N' \subset \Re^v$ such that $\N' =x_0+ \N'$. Then
\begin{align}
&\min\{d^\top x:Ax\geq b+b_0, x\in \N'\} \nn\\
&=\min\{d^\top y:Ay \geq b, y \in \N' \}+d^\top x_0.
\end{align}
\end{lemma}
\begin{proof}
The claim follows by the change of variables $y := x-x_0$.
\end{proof}
\noindent 
%Note that under our assumptions on $\N$, $\hg$ is well-defined.
%\begin{align*}
%r^*\eqdef\argmin_{r\in R^k}\norm{J^*-\Phi r}_{\mn}\,.
%\end{align*}
%where $\psi$ is a Lyapunov function as in \cref{lyap}.
\begin{lemma}\label{bestbndmn}
Let $r^*\eqdef\underset{r\in \Re^k}{\min}\parallel J^*-\Phi r\parallel_{\mn}$. Then,
\begin{align}
\norm{J^*-\Gamma J^*}_{\mn}\leq 2 \norm{J^*-\Phi r^*}_{\mn}.
\end{align}
\end{lemma}
\begin{proof}
Define $\eps = \norm{J^* - \Phi r^*}_{\mn}$ so that
$ J^*-\Phi r^* \le \eps \psi$ and $\Phi r^* - J^*\le \eps \psi$. Then, from \cref{grlpassmp}-\eqref{ass:n4} it follows that $\Phi( r^* + \eps r_0 ) = \Phi r^* + \eps \psi \ge J^* = T J^*$. From the definition of $\Gamma$ in \eqref{gamdef} and \cref{ubrem}, we know that $\Phi r^*+\eps \psi \geq \Gamma J^*\geq J^*$. The result follows by noting that $2\eps\psi\geq \Phi r^*+\eps\psi -J^*\geq \Gamma J^*-J^*\geq 0$.
\end{proof}

@@

We now show that vector $\hj$ dominates $\hv$:
\begin{lemma}\label{relation1}
The vectors $\hv,\hj$ obey $\hj\geq\hv$.
\end{lemma}
\begin{proof}
For $i\in \{1,\dots,n\}$, $c=e_i$ let $r_i$ be a solution to GRLP in \eqref{grlp}
and define $V_0\in \Re^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$.

>>>>

%!TEX root =  autocontgrlp.tex
\section{Proof of \cref{cmt2}}\label{sec:improv}
In this section we present the proof of the main result, \cref{cmt2}. 
The proof uses contraction-arguments. 
\newcommand{\G}{\Gamma}
We will introduce a novel contraction operators, $\hg: \Re^S \to \Re^S$, that captures the distortion introduced
by the extra constraint in ALP and the relaxation in LRALP, respectively. 
Then we relate the solution of LRALP to the fixed point of $\hg$.

Note that for the proof it suffices to consider the case when $\Jlro$ is finite-valued because otherwise the bound is vacuous.
Also, recall that it was assumed that $\psi$ lies in the column space of $\Phi$, while $\beta_\psi$, the $\alpha$-discounted stability of $\psi$ w.r.t. the MDP (cf. \eqref{eq:betadef}) is strictly below one. We will let $r_0\in \R^k$ be such that $\psi = \Phi r_0$.
We also assumed that the matrix $W$ is nonnegative valued, while $c$ specifies a probability distribution over $\S$: $\sum_s c(s) = 1$ and $c\in \R_+^S$.

The operator $\hg$ are defined as follows: For $J\in \Re^S$, $s\in \S$,
\begin{align*}
%(\G J)(s) & = \min\{ r^\top \phi(s) \,:\, \Phi r \ge T J ,\, r\in \Re^k \}\,,\\
(\hg J)(s) & = \min\{ r^\top \phi(s) \,:\, W^\top E \Phi r \ge W^\top E H J ,\, r\in \Re^k\}\,.
\end{align*}
Note that $(\hg J)(s)$ mimics the definition of ALP with $c = e_s$, except that the constraint $J = \Phi r$ is dropped.
%The same holds for $\hg$ in relation to LRALP.
%Letting $\F(J) = \{ \Phi r\,:\, \Phi r \ge T J, r\in \Re^k \}$ be the \emph{common} feasible set of the LP defining $(\G J)(s)$.
%It follows that for any $V\in \F(J)$, $V \ge \Gamma J$. Further, $\Gamma J \ge T J$.

Let us now recall some basic results from the theory of contraction maps.
First, let us recall the definition of contractions. Let $\norm{\cdot}$ be a norm on $\Re^S$ and $\rho>0$.
We say that the map $B: \Re^S \to \Re^S$ is $(\rho,\norm{\cdot})$-Lipschitz if for any $J,J'\in \Re^S$, $\norm{ BJ - BJ' } \le \rho \norm{J-J'}$. We say that $B$ is a \emph{$\norm{\cdot}$-contraction} with factor $\rho$ 
if it is $(\rho,\norm{\cdot})$-Lipschitz and $\rho<1$. It is particularly easy to check whether a map is a contraction map with respect to a weighted maximum norm 
if it is known to be \emph{monotone}.
Here, $B$ is said to be monotone if for any $J\le J'$, $J,J'\in \R^S$, $BJ \le BJ'$ also holds, where $\le$ is the componentwise
partial order between vectors. We start with the following characterization of monotone contractions with respect to weighted maximum norms: 
\begin{lemma}
\label{lem:maxnormmn}
Let $B:\R^S \to \R^S$, $\psi: \S \to \R_{++}$, $\beta\in (0,1)$.
The following are equivalent:
\begin{enumerate}[(i)]
\item $B$ is a monotone contraction map with contraction factor $\beta$ with respect to $\norm{\cdot}_{\psi,\infty}$.
\label{lem:item:mc}
\item For any $J,J'\in \R^S$, $t\ge 0$, $J \le J' + t \psi$ implies that $BJ \le BJ' + \beta t \psi$.
\label{lem:item:iq}
\end{enumerate}
\end{lemma}
%The proof, which essentially copies Lemma 3.1 of \cite{Kall17}, is given for completeness:
\begin{proof}
The proof is  trivial modification of the proof of Lemma 3.1 of \cite{Kall17} and is thus left as an exercise.
\if0
%Note first that for any $\eps\ge 0$, $-\eps \psi \le J - J' \le \eps \psi$ implies that $\norm{J-J'}_{\mn} \le \eps$.
Introduce $\cdot$ to denote elementwise products: Thus, $(\psi \cdot J)(s) = \psi(s) J(s)$. 
We also let $\psi^{-1}(s) = 1/\psi(s)$ and we will use the shorthand $\norm{\cdot} = \norm{\cdot}_{\mn}$.

Let us first prove \eqref{lem:item:mc} $\Rightarrow $ \eqref{lem:item:iq}. 
Thus, assume that $B$ is a monotone contraction
map with factor $\beta$. Take any $J,J'$, $t>0$, $J \le J'+ t\psi$. 
We have $BJ = B(J + t \psi) - B J' + B J' \le (\psi^{-1} \cdot (B(J + t \psi) - B J' ))\cdot \psi + BJ'
\le \norm{B(J+t\psi) - BJ'} \psi + BJ' \le \beta t \norm{J-J'} \psi +  BJ'$.

For the reverse direction, note that monotinicity follows by taking $t=0$.
Now, let $\eps = \norm{J-J'}$. Then, $J \le J'+ \eps \psi$ and $J' \le J+\eps \psi$.
By monotonicity and the assumed property of $B$ (using $t=\eps\ge 0$), 
$-\beta \eps \psi \le BJ - BJ' \le \beta \eps \psi$, which implies
that $\norm{BJ - BJ'} \le \beta$.
\fi
\end{proof}
\begin{corollary}
\label{maxnormmn}
\label{cor:maxnormmn}
If $B$ is monotone and there exists some $\beta\in [0,1)$ such that for any $J\in \Re^S$ and $t>0$,
\begin{align}
\label{eq:shiftmn}
B( J + t \psi) \le B J + \beta t \psi
\end{align} 
then $B$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta$.
\end{corollary}
\begin{proof}
Let $J,J'\in \R^S$, $t\ge 0$ and assume that $J\le J' + t \psi$. By monotonicity $BJ \le B(J'+ t \psi)$, while
by~\eqref{eq:shiftmn}, $B(J'+t\psi) \le BJ' + \beta t \psi$. Hence, $BJ \le BJ' + \beta t \psi$. 
This shows that \eqref{lem:item:iq} of \cref{lem:maxnormmn} holds. 
Hence, by this lemma, $B$ is a contraction with factor $\beta$ with respect to $\norm{\cdot}_{\mn}$.
\end{proof}
\if0
\begin{proof}
First, we show that for any $t\ge 0$,  $J\in \Re^n$,
$B( J - t \psi) \ge B J - \beta t \psi$ also holds.
To see this define $J' = J-t\psi$. Then, $J = J'+t\psi$, hence $B J \le B J' + \beta t \psi$. Reordering this inequality gives the result.
Let $\eps = \norm{J_1 - J_2}_{\mn}$, where $J_1,J_2\in \Re^n$ are arbitrary.
Then $J_2 - \eps \psi \le J_1 \le J_2 + \eps \psi$. 
By the monotonicity of $B$,
$B(J_2 - \eps \psi) \le B J_1 \le B(J_2 + \eps \psi)$. 
Using~\eqref{eq:shiftmn}, we get 
$B J_2 - \beta \eps \psi \le B J_1 \le B J_2 + \beta \eps \psi$, i.e., $-\beta \eps \psi \le B J_1 - B J_2 \le \beta \eps \psi$, from which the result follows.
\end{proof}
\fi

@@

Let us now return to the proof of our main result. Recall that the goal is to bound 
$\norm{J^*-\Jlr}_{1,c}$ through relating this deviations from the fixed point of $\hg$, which was promised to be a contraction.
Let us thus now prove this.
%\emph{Since all $1$-norms will use the same weighting $c$, we will abbreviate $\norm{\cdot}_{1,c}$ to $\norm{\cdot}_1$. Similarly, since all maximum norms use the same weighting $\psi$, we will abbreviate $\norm{\cdot}_{\infty,\psi}$ to $\norm{\cdot}_{\infty}$.}
For this, it suffices to show that $\hg$ satisfies the conditions of \cref{cor:maxnormmn}.
In fact, we will see this holds with $\beta =\beta_\psi$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}\label{tgmonotone}\label{gshiftmn}
The operator $\hg$ satisfies the conditions of \cref{cor:maxnormmn} with $\beta =\beta_\psi$, and is thus a 
$\norm{\cdot}_{\mn}$-contraction with coefficient $\beta_\psi$. 
%For $J_1, J_2\in \Re^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.
\end{proposition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proof}
First, note that (as it is well known) $H$ is monotone (all 
the $P_a$ matrices in the definition of $H$ are nonnegative valued) 
and that it satisfies an inequality similar to \eqref{eq:shiftmn}: For any $t\ge 0$, $J\in \R^S$,
\begin{align}\label{eq:psilin}
\begin{split}
%T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi,\\
H(J+ t \psi ) \le HJ + \beta_{\psi}\,t\,  E  \psi\,.
\end{split}
\end{align}
This follows again because our assumption on $\psi$ implies that for any $a\in \A$, $\alpha P_a \psi \le \beta_{\psi} \psi$.

Let us now prove that $\hg$ is monotone. 
Given $J\in \Re^S$, let $\F'(J)\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \Re^k\,\}\,$. 
Choose any $s\in \S$. Since $J_1\leq J_2$, $W$ is nonnegative valued and $H$ is monotone, 
%\Cref{tprop}-\eqref{monotone} and \cref{grlpassmp}-\eqref{wassmp} 
we have $W^\top H J_1\leq W^\top H J_2$. 
Hence, $\F_{J_2} \subset \F_{J_1}$ 
and thus $(\hg J_1)(s) \le (\hg J_2)(s)$.  Since $s$ was arbitrary, monotonicity of $\hg$ follows.

Let us now turn to proving that \eqref{eq:shiftmn} holds with $\beta =\beta_\psi$.
By definition, for $s\in \S$, $t\ge 0$, $J\in \R^S$, 
$(\hg (J+t\psi) )(s) = \min\{ r^\top \phi(s) \,:\, W^\top E\Phi r \ge W^\top H(J+t\psi), r\in \Re^k \}$.
By \eqref{eq:psilin}, 
$H(J+t\psi) \le HJ + t \beta_\psi E \psi$ 
and hence $W^\top H(J+t\psi) \le W^\top (HJ + t \beta_\psi E \psi)$. 
Thus,
$(\hg (J+t\psi) )(s) \le  \min\{ r^\top \phi(s)\,:\, W^\top E\Phi r \ge W^\top (HJ+t\beta_\psi E \psi), r\in \Re^k \}$.

To finish, we need the following elementary observation:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{claim}\label{lpsol}
Let $A\in \Re^{u\times v}$, $b\in \Re^u,d\in \Re^v$ and $b_0=Ax_0$ for
some $x_0 \in \Re^v$. % $\N' \subset \Re^v$ such that $\N' =x_0+ \N'$. 
Then
\begin{align*}
\begin{split}
\MoveEqLeft \min\{d^\top x:Ax\geq b+b_0, x\in \Re^v\} \nn\\
&=\min\{d^\top y:Ay \geq b, y \in \Re^v \}+d^\top x_0.
\end{split}
\end{align*}
\end{claim}
\begin{proof}[Proof of \cref{lpsol}]
The claim follows by the change of variables $y := x-x_0$.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Now, using \Cref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $d=\phi(s)$, $b_0=t\beta_\psi W^\top E \psi$
and $x_0=t \beta_\psi r_0$,  thanks to $\Phi r_0 = \psi$ we have $A x_0 = b_0$.
Hence the desired statement follows from the claim.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Let us now return to bounding $\norm{J^*-\Jlr}_{1,c}$.
For $x\in \Re$, let $(x)^-$ be the negative part of $x$: $(x)^- = \max(-x,0)$. Then, $|x| = x + 2 (x)^-$. For a vector $J\in \R^S$, 
we will write $(J)^-$ to denote the vector obtained by applying the negative part componentwise.
We consider the decomposition
\begin{align}
\label{eq:maindec}
\norm{\Jlr-J^*}_{1,c} = c^\top ( \Jlr - J^* ) + 2c^\top ( \Jlr - J^* )^-\,.
\end{align}
Let $\hv$ be the fixed point $\hg$. We know claim the following:
\begin{claim}
We have $\Jlr \ge \hv$, $c^\top \Jalp \ge c^\top \Jlr$.
\end{claim}
\begin{proof}
The inequality $c^\top \Jalp \ge c^\top \Jlr$  follows immediately from the definitions of $\Jalp$ and $\Jlr$.

To prove the first part let $s\in \S$,  $c=e_s$ and let $r_s$ be a solution to LRALP in \eqref{grlp}.
For $s\in \S$, let $V_0(s)= \min_{s'\in \S} r_{s'}^\top \phi(s)$.

It suffices to show that $V_1\eqdef \hg V_0 \le V_0 \le \hj$.
Indeed, if this holds then
$V_{n+1} = \hg V_n$, $n\ge 1$, satisfies $V_{n+1}\le V_n$ and $V_n \to \hv$ as $n\to\infty$
since $\hg$ is a monotone contraction mapping.

Since  $r_{s'}^\top \phi(s) \ge r_s^\top \phi(s)$ %$(\Phi r_{s'})(s) \ge (\Phi r_s)(s)$
 also holds for any $s,s'\in \S$,
we have $V_0(s)  = r_s^\top \phi(s)$. %$(\Phi r_s)(s)$. 
Also, since $\hj(s) \ge r_s^\top \phi(s)$, % (\Phi r_s)(s)$,$s\in \S$
it follows that $\hj\geq V_0$. 
Now,  fix some $s\in \S$ and
define $r'_{e_s,V_0}$ be the solution to the linear program defining $(\hg V_0)(s)$.
We need to show that $V_1(s)=(\hg V_0)(s) = ( r'_{e_s,V_0})^\top \phi(s) \leq V_0(s)$. 
By the definition of $r'_{e_s,V_0}$ we know that $( r'_{e_s,V_0})^\top \phi(s) \le r^\top \phi(s)$ %$(\Phi r)(s)$
holds for any $r\in \Re^k$ such that $W^\top E \Phi r \ge W^\top H V_0$. 
Thus, it suffices to show that $r_s$ satisfies $W^\top E \Phi r_s \ge W^\top H V_0$. 
By definition, $r_s$ satisfies $W^\top E \Phi r_s \ge W^\top H \Phi r_s$.
Hence, by the monotone property of $H$ and since $W$ is nonnegative valued, % and \cref{grlpassmp}-\eqref{wassmp} 
it is sufficient if $\Phi r_s \ge V_0$.
This however follows from the definition of $V_0$.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Thanks to the previous claim, $(\Jlr - J^*)^- \le (\hv - J^*)^-$ and $c^\top \Jlr \le c^\top \Jalp$. Hence, 
from \eqref{eq:maindec} we get
\begin{align*}
%\label{eq:maindec2}
\norm{\Jlr-J^*}_{1,c} \le c^\top\!( \Jalp - J^* ) + 2c^\top\!( \hv - J^* )^-\,.
\end{align*}
By Theorem 3 of \cite{ALP}, the first term is bounded by $2 \frac{c^\top \psi}{1-\beta_\psi} \epsilon$, where
recall that $\epsilon = \inf_{r} \norm{J^* - \Phi r}_{\mn}$. Hence, it remains to bound the second term.

For this, note that for any $J\in \R^S$, 
$(J)^-\le |J|$
and also that $\norm{J}_{1,c} \le c^\top \psi \norm{ J }_{\mn}$. Hence, we switch to bounding 
$\norm{J^* - \hv }_{\mn}$.
A standard contraction argument gives
\begin{align*}
\norm{J^* - \hv }_{\mn}
& =   \norm{ J^* - \hg J^ + \hg J^* -\hg \hv }_{\mn} \\
& \le \norm{ J^* - \hg J^*}_{\mn} + \norm{\hg J^* - \hv }_{\mn} \\
& \le \norm{ J^* - \hg J^*}_{\mn} + \beta_\psi \norm{\hg J^* - \hv }_{\mn}\,.
\end{align*}
Reordering and using another triangle inequality we get
\begin{align*}
\norm{J^* - \hv }_{\mn} \le \frac{
\norm{J^* - \Jalpo}_{\mn} + \norm{ \Jalpo - \hg J^* }_{\mn}
}{1-\beta_\psi}\,.
\end{align*}
We bound the term $\norm{J^* - \Jalpo}_{\mn}$ in the following lemma:
\begin{lemma}\label{bestbndmn}
We have
\begin{align}
\norm{J^*-\Jalpo}_{\mn}\leq 2 \epsilon\,,
\end{align}
where recall that $\epsilon = \inf_{r\in \Re^k} \norm{ J^*-\Phi r }_{\mn}$. 
\end{lemma}
\begin{proof}
Let $r^*\eqdef \argmin_{r\in \Re^k} \norm{ J^*-\Phi r }_{\mn}$. 
First, notice that $\Jalpo \ge J^*$.
Hence, $0\le \Jalpo - J^*$.
Now let $r' = r^* + \epsilon r_0$. Then, 
$\Phi r' = \Phi r^* + \epsilon \psi \ge J^*$, where the equality follows by the definition of $r_0$ and
the inequality follows by the definition of $\epsilon$.
Hence, $r'$ is in the feasible set of the LP defining $\Jalpo$ and thus $\Jalpo \le \Phi r'$.
Thus, $0\le \Jalpo - J^* \le \Phi r^* - J^* + \epsilon \psi$. Dividing componentwise by $\psi$,
taking absolute value and then taking maximum of both sides gives the result.
\end{proof}
The proof of the main result is finished by noting that $\hg J^* = \Jlro$ and the chaining the inequalities we derived.

\if0
Now, recall further that if $B:\R^S \to \R^S$ is a $(\beta,\norm{\cdot})$-contraction then it has a unique fixed point $J^*_B\in \R^S$ (i.e., $B J^*_B= J^*_B$). Further, for any $J\in \R^S$,
\begin{align}
\label{eq:csdw}
\frac{\norm{J-J^*_B}}{1-\beta} \le \norm{ BJ - J } \le (1+\beta) \norm{J-J^*_B}\,.
\end{align}
That is, $\norm{BJ-J}$ is closely tied to the distance of $J$ from $J^*_B$.%
\footnote{This is also a standard result. The upper bound can be obtained using a triangle inequality and exploiting that $J^*_B$ is a fixed point of $B$ which is a contraction. The lower bound follows by writing $J - J^*_B = (\sum_{k=0}^n B^k J - B^{k+1} J ) + B^{n+1} J - B^{n+1} J^*_B$, taking norms using the triangle inequality together with the contraction property of $B$ and finally letting $n\to \infty$.}
We will repeatedly apply this inequality.

Let $\hv$ be the fixed point $\hg$.
Then, by the triangle inequality,
\begin{align*}
\norm{J^*-\Jlr}_{1,c} \le \norm{J^*-\hv}_{1,c} +\norm{\hv-\Jlr}_{1,c}\,.
\end{align*}
Let us first bound the second term. Recall that $\Jlr = \Phi \rlr$.

\if0
We note in passing that if \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \Re^n$ and $t>0$,
\begin{align}\label{eq:psilin}
\begin{split}
T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi,\\
H(J+ t \psi ) \le HJ + E \beta_{\psi}\,t\,  \psi\,.
\end{split}
\end{align}
\fi
%\input{schematic}

\noindent 
%Note that under our assumptions on $\N$, $\hg$ is well-defined.
%\begin{align*}
%r^*\eqdef\argmin_{r\in R^k}\norm{J^*-\Phi r}_{\mn}\,.
%\end{align*}
%where $\psi$ is a Lyapunov function as in \cref{lyap}.

@@
